Labor Markets and Technological Change: Evidence from Electronic Health Records

### 2022-11-07 Paper/Paper.tex
Updates from Overleaf

\begin{figure}[H]
\centering
   \begin{subfigure}[b]{0.3\textwidth}
   \includegraphics[width=0.8\textwidth]{retire_plot_ages}
   \caption{}
   \label{fig:Ng1} 
\end{subfigure}

\\

\begin{subfigure}[b]{0.3\textwidth}
   \includegraphics[width=0.8\textwidth]{Nvariousg2}
   \caption{}
   \label{fig:Ng2}
\end{subfigure}
\caption{(a) Numerical solutions for the small-time system with a constant-curvature body shape showing the scaled leading-order veritcal reaction force $N_0$ versus the scaled body mass $M$ for various values of $g$. Again, $I=M$ for definiteness and $A=0.7$. (b) As for (a) but over a wider range of values of $M,I$.}
\end{figure}

\begin{figure}[ht!]
    \centering
    \captionsetup{width=.85\linewidth}
    \caption{Effect of EHR Exposure on Retirement}
    \includegraphics[scale=.5]{Objects/retire_plot.pdf}
    \label{fig:retirefirst}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} The top panel shows average group time treatment effects aggregated over groups to an event study plot. The bottom show these results for different subgroups of physicians by age. The p-value listed for each graph corresponds to a Wald test for pre-trends. Confidence intervals shown are simultaneous confidence bands accounting for multiple hypothesis testing. Overall ATT for all, $<$ 60, $>=$ 60 with SE in parentheses: 0.003 (0.0009), 0.002 (0.001), 0.006 (0.003), respectively.}}
\end{figure}

>>>>

\begin{figure}[ht!]
\centering
    \captionsetup{width=.85\linewidth}
    \caption{Effect of EHR Exposure on Retirement}
   \begin{subfigure}[]{.8\textwidth}
   \includegraphics[scale=.5]{Objects/retire_plot_all.pdf}
   \caption{}
   \label{fig:Ng1} 
\end{subfigure}

\begin{subfigure}[]{.8\textwidth}
   \includegraphics[scale=.5]{Objects/retire_plot_ages.pdf}
   \caption{}
   \label{fig:Ng2}
\end{subfigure}
\vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} Panel (a) shows average group time treatment effects aggregated over groups to an event study plot. Panel (b) shows these results for different subgroups of physicians by age. The p-value listed for each graph corresponds to a Wald test for pre-trends. Confidence intervals shown are simultaneous confidence bands accounting for multiple hypothesis testing. ATT for all, $<$ 60, $>=$ 60 with SE in parentheses: 0.003 (0.0009), 0.002 (0.001), 0.006 (0.003), respectively.}}
\end{figure}
